---
title: "Project_3_ShubhamTomar"
output: html_document
date: "2022-10-09"
---

```{r}
library(tidyverse)
library(dplyr)
library(lubridate)
library(stringr)
```


```{r}
b_lyrics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-29/beyonce_lyrics.csv')
ts_lyrics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-29/taylor_swift_lyrics.csv')
sales <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-29/sales.csv')
```




#Part 1: Explore album sales

##Part 1A: Data wrangling
```{r}
sales_1 <- sales %>%
   mutate(released = str_remove(released, "\\(.*")) 

x<- mdy(sales_1$released)

sales_1 <- sales_1 %>% 
  mutate(released = x)
 
sales_2 <- sales_1 %>% 
  mutate(country = fct_collapse(sales_1$country, "FR"= c("FRA", "FR"), "World"= c("WW", "World"))) %>%
  group_by(country) %>%
  filter(country %in% c("US", "UK", "World"))

sales_2[c("sales")] <- sales_2[c("sales")]/1e6

sales_2
```

##Part 1B: Only US Albums
```{r}
sales_3 <- sales_2 %>% group_by(country) %>%
  filter(country %in% c("US"))

release_date <- sales_3$released
today <- ymd(20221013)
interval(release_date, today)
years_since_release <- interval(release_date, today) %>%
  as.numeric('years') %>% 
  round(digits = 0)

sales_4 <- sales_3 %>% mutate(years_since_release)

sales_4 %>%
  summarise(years_since_release, median = median(years_since_release), oldest = max(years_since_release), newest= min(years_since_release))
```

##Part 1C: Percent stacked barchart:
```{r}
library(dplyr)

graph_data <- sales_2 %>%
  group_by(artist, country) %>%
  summarise(TotalSales=sum(sales))

library(ggplot2)
graph_data %>% 
  ggplot(aes(fill= country ,y= TotalSales, x= artist)) +
  geom_bar(position="fill", stat="identity") +
  labs(title = "Percent stacked barchart", x= "Artist", y= "Percentage of sales of studio albums (in millions)")
  
```

##Part 1D: Sales

```{r}
sales_5 <- sales_2 %>%
           filter(country== 'World')

sales_5 %>%
  ggplot(aes(x= sales, y=fct_reorder(.f = title, .x =sales), fill= artist ))+
  geom_bar(stat = "identity") +
  labs(title = "Sales of studio albums", x= "Sales", y= "Album titles")

```
##Part 1E: Scatter plot
```{r}
scat_sale <- ggplot(sales_2, aes(x=released, y=sales, col=artist)) +
     geom_point()
scat_sale + 
  facet_grid(. ~ country) +
  labs(title = "Scatter plot across countries", x= "years", y= "sales of studio albums (in millions)")
```


#Part 2: Exploring sentiment of lyrics
```{r}
library(tidytext)
```

###Part 2A: hello and goodbye Taylor
```{r}
ts_lyrics_token<-
  ts_lyrics %>% 
     unnest_tokens(output = line, 
                   input = Lyrics, 
                   token = "lines") %>%
     mutate(linenumber = row_number())

hello_ts<- str_subset(ts_lyrics_token$line, "hello")
goodbye_ts <- str_subset(ts_lyrics_token$line, "goodbye")

hello_ts
summary(hello_ts)

goodbye_ts
summary(goodbye_ts)
```


###Part 2B hello and goodbye Beyonce
```{r}
hello_b<- str_subset(b_lyrics$line, "hello")
goodbye_b<- str_subset(b_lyrics$line, "goodbye")

hello_b
summary(hello_b)

goodbye_b
summary(goodbye_b)
```


###Part 2C b_lyrics dataset, barchart and Wordcloud

```{r}
b_lyrics_token <- 
  b_lyrics %>% 
     unnest_tokens(output = word, 
                   input = line, 
                   token = "words") %>%
  mutate(linenumber = row_number()) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
 inner_join(get_sentiments("bing"))
```

####sorting row from most frequent to least frequent, and filtering top 25 words
```{r}
b_lyrics_token<- arrange(b_lyrics_token, desc(n)) %>%
  head(b_lyrics_token, n=25)
b_lyrics_token
```


```{r}
b_lyrics_token %>%
  mutate(word = fct_reorder(word, n)) %>%
  ggplot(aes(x = n, y = word, fill= sentiment)) +
  geom_col(show.legend = TRUE) +
  labs(y= "Top words", x= "Frequency of words")
```

####WordCloud
```{r}
library(wordcloud)
library(RColorBrewer)
library(tm)
pal = brewer.pal(6, "RdGy")
```

```{r}
b_lyrics_token %>% 
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, min.freq = 1, scale = c(2, 0.5), random.color = TRUE, colors = pal))
```
, max.words=100, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, “Dark2”))



###Part 2D ts_lyrics dataset, barchart and Wordcloud

```{r}
ts_lyrics_wtoken <- 
  ts_lyrics %>% 
     unnest_tokens(output = word, 
                   input = Lyrics, 
                   token = "words") %>%
  mutate(linenumber = row_number()) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
 inner_join(get_sentiments("bing"))
```

####sorting row from most frequent to least frequent, and filtering top 25 words
```{r}
ts_lyrics_wtoken<- arrange(ts_lyrics_wtoken, desc(n)) %>%
  head(ts_lyrics_wtoken, n=25)
ts_lyrics_wtoken
```


```{r}
ts_lyrics_wtoken %>%
  mutate(word = fct_reorder(word, n)) %>%
  ggplot(aes(x = n, y = word, fill= sentiment)) +
  geom_col(show.legend = TRUE) +
  labs(y= "Top words", x= "Frequency of words")
```

####WordCloud
```{r}
library(wordcloud)
library(RColorBrewer)
library(tm)
pal = brewer.pal(6, "RdGy")
```

```{r}
ts_lyrics_wtoken %>% 
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, min.freq = 1, scale = c(2, 0.5), random.color = TRUE, colors = pal))
```
, max.words=100, random.order=FALSE, rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, “Dark2”))


###Part 2E ts_lyrics_afinn

```{r}
get_sentiments("afinn")
```

```{r}
ts_lyrics_wtoken <- 
  ts_lyrics %>% 
     unnest_tokens(output = word, 
                   input = Lyrics, 
                   token = "words") %>%
  mutate(linenumber = row_number()) %>%
  anti_join(stop_words) %>%
  count(word, Album, sort = TRUE) %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(Album) %>%
  summarise(mean= mean(value))

ts_lyrics_wtoken
```
####Joining 2 datasets
```{r}
sales_2 <- sales_2 %>% rename_at("title", ~"Album")

ts_plot<- inner_join(x= sales_2,y= ts_lyrics_wtoken, by= "Album")
```

#### ggplot
```{r}
ts_plot %>%
  ggplot(aes(x = released, y = mean, color= Album)) + 
  geom_point(aes(size= sales)) +
  labs(title= "Sentiments of Taylor Swift's songs over the years" ,subtitle= "Analysis of taylor songs by Shubham" ,x= "Release date", y= "Average score") +
  geom_hline(yintercept = 0) 
```
#####“How has the sentiment of Taylor Swift’s albums have changed over time?”
#####Above plot shows average sentiment score in albums of Taylor Swift. We can see that average score is decreasing over the years and thus her songs are getting negative.